First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-02-08 eg6-letters/coherent/dvcs_he4_prl.tex
Minor update for x vs. x_B confusions

The coherent nuclear DVCS channel is experimentally difficult due to  
its small cross section and the necessity to ensure the target remains 
intact while emitting a hard photon ($eA \rightarrow e' A' \gamma$). Figure 
\ref{fig:diags} illustrates the hand bag diagram for coherent DVCS on 
$^4$He. Similar to the proton case, at large virtual photon's 4-momentum square 
$Q^2=-(k-k')^{2}$ and small squared momentum transfer $t=(p-p')^{2}$,
the DVCS handbag diagram can be factorized into two parts 
\cite{Freund_Collins,Ji_Osborne}. The hard part includes the photon-quark 
interaction and is calculable with perturbative QED.  The non-perturbative 
part is parametrized in terms of GPDs, which embed the partonic structure of 
the hadron. The GPDs depend on the three variables $x_B$, $\xi$ and $t$, which are 
indicated in Figure \ref{fig:diags} for the DVCS process. In DVCS, $\xi$ can 
be related to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
where $x_B=\frac{Q^2}{2M\nu}$ with $M$ the proton mass and 
$\nu=E_e-E_{e^\prime}$. One can access $t$ as the squared momentum 
transferred to the target, however $x_B$ cannot be experimentally 
accessed in a DVCS reaction. Hence, we measure only complex Compton Form 
Factors (CFF) \cite{Guidal:2013rya} defined as:
\begin{align}
\begin{split}
\Re e(&\mathcal{H}_{A}) = \\
    &\mathcal{P} 
\int_{0}^{1}dx[H_A(x,\xi,t)-H_A(-x,\xi,t)] \, C^{+}(x,\xi), 
\end{split} \\
\Im m(&\mathcal{H}_{A}) = H_A(\xi,\xi,t)-H_A(-\xi,\xi,t),
\end{align}
with $H_A$ the GPD, $\mathcal{P}$ 
the Cauchy principal value integral, and $C^{+}(x,\xi)$ a coefficient function 
($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$).

>>>>

The coherent nuclear DVCS channel is experimentally difficult due to  
its small cross section and the necessity to ensure the target remains 
intact while emitting a hard photon ($eA \rightarrow e' A' \gamma$). Figure 
\ref{fig:diags} illustrates the hand bag diagram for coherent DVCS on 
$^4$He. Similar to the proton case, at large virtual photon's 4-momentum square 
$Q^2=-(k-k')^{2}$ and small squared momentum transfer $t=(p-p')^{2}$,
the DVCS handbag diagram can be factorized into two parts 
\cite{Freund_Collins,Ji_Osborne}. The hard part includes the photon-quark 
interaction and is calculable with perturbative QED.  The non-perturbative 
part is parametrized in terms of GPDs, which embed the partonic structure of 
the hadron. The GPDs depend on the three variables $x$, $\xi$ and $t$, which are 
indicated in Figure \ref{fig:diags} for the DVCS process. In DVCS, $\xi$ can 
be related to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
where $x_B=\frac{Q^2}{2M\nu}$ with $M$ the proton mass and 
$\nu=E_e-E_{e^\prime}$. One can access $t$ as the squared momentum 
transferred to the target, however $x$ cannot be experimentally 
accessed in a DVCS reaction. Hence, we measure only complex Compton Form 
Factors (CFF) \cite{Guidal:2013rya} defined as:
\begin{align}
\begin{split}
\Re e(&\mathcal{H}_{A}) = \\
    &\mathcal{P} 
\int_{0}^{1}dx[H_A(x,\xi,t)-H_A(-x,\xi,t)] \, C^{+}(x,\xi), 
\end{split} \\
\Im m(&\mathcal{H}_{A}) = H_A(\xi,\xi,t)-H_A(-\xi,\xi,t),
\end{align}
with $H_A$ the GPD, $\mathcal{P}$ 
the Cauchy principal value integral, and $C^{+}(x,\xi)$ a coefficient function 
($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$).
